Creating the ``r params$package_name`` R package

### 2025-07-09 create-FSHybridPLS.Rmd
confirmed correlation maximization

### main function: get_pls_comp
Computes the first PLS component from a hybrid predictor and response vector using regularization.

- Inputs
  - **`W`**: A `predictor_hybrid` object with functional and scalar predictors.
  - **`y`**: A numeric response vector of length equal to `W$n_sample`.
  - **`L`**: A Cholesky decomposition of a positive definite regularization matrix.
- Output: 
  - `xi_hat`: The first PLS component as a `predictor_hybrid` object
  - `E`: The matrix `inv(L) %*% V_star %*% t(inv(L))`
  - `V_star`: Cross-covariance matrix between predictors and response
  - `eigen_val`: Leading eigenvalue of `E`
```{r}
#' Compute the First PLS Component from a Hybrid Predictor
#'
#' Computes the coefficients of the first Partial Least Squares (PLS) component based on 
#' a hybrid predictor object and a response vector, using a regularized generalized eigenvalue problem.
#'
#' @param W A \code{predictor_hybrid} object containing both functional and scalar predictors.
#' @param y A numeric response vector of length equal to the number of samples in \code{W}.
#' @param L cholesky decompisition of a regularization matrix (typically positive definite) used in the generalized eigenproblem.
#'
#' @return A list with the following elements:
#' \describe{
#'   \item{\code{xi_hat}}{The estimated first PLS component as a \code{predictor_hybrid} object.}
#'   \item{\code{E}}{The generalized eigenvalue problem matrix \code{E = inv(L) V* t(inv(L))}.}
#'   \item{\code{V_star}}{The cross-covariance matrix between predictors and response.}
#'   \item{\code{eigen_val}}{The leading eigenvalue of \code{E}.}
#' }
#'
#' @export
get_pls_comp <- function(W, y, L){

@@

  invL <- Matrix::chol2inv(L)
  A <- V_star %*% t(invL)       # A = V* × t(inv(L))
  E <- invL %*% A               # E = inv(L) × A

@@

  xi_star <- t(invL) %*% e      # xi_star solves t(L) xi = e
  xi_hat <- predictor_hybrid_from_coef(format = W, coef = xi_star)

  return(list(
    xi_hat = xi_hat,
    E = E,
    V_star = V_star,
    eigen_val = eigen_result$values[1]
  ))
}
```

@@

@@

### get_pls_comp_simple
```{r}
#' Compute First PLS Component (Direct Hilbert Averaging)
#'
#' Computes the first PLS component as a normalized weighted average of predictor objects,
#' where weights are given by the centered response values.
#'
#' @param W A `predictor_hybrid` object containing `n_sample` observations.
#' @param y A numeric response vector of length `n_sample`.
#'
#' @return A normalized `predictor_hybrid` object representing the first PLS component.
#' @export
get_pls_comp_simple <- function(W, y) {
  n <- W$n_sample
  if (length(y) != n) stop("Length of y must match number of samples in W.")

  # Center the response (optional, but often improves interpretability)
  y_centered <- y - mean(y)

  # Initialize zero element
  xi_sum <- scalar_mul.predictor_hybrid(subset_predictor_hybrid(W, 1), y_centered[1])

  # Accumulate weighted sum: sum_i y_i * W_i
  for (i in 2:n) {
    Wi <- subset_predictor_hybrid(W, i)
    xi_sum <- add.predictor_hybrid(xi_sum, Wi, alpha = y_centered[i])
  }

  # Normalize
  xi_sum <- scalar_mul.predictor_hybrid(xi_sum, 1/n)
  norm_val <- sqrt(inprod.predictor_hybrid(xi_sum))
  xi_hat <- scalar_mul.predictor_hybrid(xi_sum, 1 / norm_val)

  return(xi_hat)
}

@@

# --- Step 5: Run eigen-based PLS ---
W_template <- W  # prevent mutation
pls_eig_result <- get_pls_comp(W, y, L)
xi_hat_eig <- pls_eig_result$xi_hat

# --- Step 6 (Revised): Manually compute direct PLS component and wrap with predictor_hybrid_from_coef ---

# Scalar part

# Functional part: stack the weighted coefficients
func_weighted_vec <- unlist(lapply(functional_list, function(fd_j) {
  coef(fd_j) %*% y  # nbasis × 1
}))

# Full coefficient vector
Z_weighted <- colSums(Z * y)

xi_raw_vec <- c(func_weighted_vec, Z_weighted)

# Wrap into predictor_hybrid object using format template
xi_hat_direct <- predictor_hybrid_from_coef(format = W_template, coef = xi_raw_vec)

@@

xi_new <- get_xi_direct(W, y)

# --- Step 7: Compare and evaluate ---
ip <- inprod.predictor_hybrid(xi_hat_eig, xi_hat_direct)
norm1 <- sqrt(inprod.predictor_hybrid(xi_hat_eig))
norm2 <- sqrt(inprod.predictor_hybrid(xi_hat_direct))
cos_theta <- ip / (norm1 * norm2)

>>>>

### main function (wrapper: get_pls_comp
Computes the first PLS component from a hybrid predictor and response vector using regularization.

- Inputs
  - **`W`**: A `predictor_hybrid` object with functional and scalar predictors.
  - **`y`**: A numeric response vector of length equal to `W$n_sample`.
  - **`L`**: A Cholesky decomposition of a positive definite regularization matrix.
- Output: 
  - `xi_hat`: The first PLS component as a `predictor_hybrid` object
  - `E`: The matrix `inv(L) %*% V_star %*% t(inv(L))`
  - `V_star`: Cross-covariance matrix between predictors and response
  - `eigen_val`: Leading eigenvalue of `E`
```{r}
#' Compute the First PLS Component from a Hybrid Predictor
#'
#' Computes the coefficients of the first Partial Least Squares (PLS) component based on 
#' a hybrid predictor object and a response vector, using a regularized generalized eigenvalue problem.
#'
#' @param W A predictor_hybrid object containing both functional and scalar predictors.
#' @param y A numeric response vector of length equal to the number of samples in W.
#' @param L cholesky decompisition of a regularization matrix (typically positive definite) used in the generalized eigenproblem.
#'
#' @return A list with the following elements:
#'
#'   xi_hat: The estimated first PLS component as a predictor_hybrid object.
#'   E: The generalized eigenvalue problem matrix E = inv(L) V* t(inv(L)).
#'   V_star: The cross-covariance matrix between predictors and response.}
#'   eigen_val: The leading eigenvalue of E.
#' 
#'
#' @export
get_pls_comp <- function(W, y, L){

@@

  #invL <- Matrix::chol2inv(L)
  invL <- solve(L)
  A <- V_star %*% t(invL)       # A = V* × t(inv(L))
  E <- invL %*% A               # E = inv(L) × A

@@

  xi_star <- t(invL) %*% e      # xi_star solves t(L) xi = e
  xi_hat <- predictor_hybrid_from_coef(format = W, coef = xi_star)
  return(list(
    xi_hat = xi_hat,
    E = E,
    V_star = V_star,
    eigen_val = eigen_result$values[1]
  ))
}
```

@@

### helper: get_xi_hat_linear
```{r}
get_xi_hat_linear <- function(W, y){
  n <- W$n_sample
  K <- W$n_functional
  d = list()
  for (i in 1:K){  ## tPhi_tC : C multiplied by Phi. Scalable to arbitrary K
    Ct <- W$functional_list[[i]]$coefs
    Phi <- W$gram_list[[i]]
    rhs <-  t(Phi) %*% Ct %*% y
    d[[i]] <- solve(Phi, rhs)
  }
  d[[K+1]] <- t(W$Z) %*% y
  d_vec <- do.call(c, d)  # or: unlist(d)
  return(d_vec)
}
```

@@

@@

# --- Step 5: Run eigen-based PLS ---
W_template <- W  # prevent mutation

pls_eig_result <- get_pls_comp(W, y, L)
xi_hat_eig <- pls_eig_result$xi_hat

xi_hat_lin <- get_xi_hat_linear(W, y)

# Wrap into predictor_hybrid object using format template
xi_hat_direct <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin)

@@

# --- Step 7: Compare and evaluate ---
ip <- inprod.predictor_hybrid(xi_hat_eig, xi_hat_direct)
norm1 <- sqrt(inprod.predictor_hybrid(xi_hat_eig))
xi_hat_eig <- scalar_mul.predictor_hybrid(xi_hat_eig,  1 / norm1)

norm2 <- sqrt(inprod.predictor_hybrid(xi_hat_direct))
cat("norm 1", norm1,  "\n")
cat("norm 2", norm2,  "\n")

cos_theta <- ip / (norm1 * norm2)
